QECO: A QoE-Oriented Computation Offloading Algorithm based on Deep Reinforcement Learning for Mobile Edge Computing

### 2024-10-16 Revision/Paper_Rev.tex
Rev_V6.1

\begin{table*}[htbp]\textcolor{blue}{
		\renewcommand{\arraystretch}{0.7}
		\captionsetup{name=TABLE}
		\caption{Comparison of Related Works}
		\scalebox{1}{%
			\begin{tabular}{ lp{2.2cm}p{3cm}p{3.4cm}p{0.7cm}p{2cm}p{3.2cm}l} 
				\toprule
				\textbf{Paper} & \textbf{Scenario} &  \textbf{Problem} &  \textbf{Objective} &  \textbf{Model} & \textbf{Method} &  \textbf{Drawbacks}  \\ \midrule
				\cite{liao2023online} & Queuing-based MEC & Online computation offloading & Minimize computation delay and energy consumption & MDP & DDQN & Only for a singel MEC system model  \\\midrule
				\cite{zhou2021deep} & heterogeneous MEC & Resource allocation and computation offloading & Minimize energy consumption of the entire system & MDP & DDQN & Only for a singel MEC system model \\\midrule				
				%\cite{huang2019deep} & Wireless-powered MEC & Computation offloading and resource allocations & Maximize computation rate & MIP & DQN & Not consider delay-sensitive tasks \\\midrule
				\cite{wu2024privacy} & MEC-based IIoT  & Joint power allocation and computation offloading  & Optimization of privacy protection and quality of service. & MDP & Multi-agent actor-critic network& Not take user's demand into consideration \\\midrule
				\cite{zhao2019deep} & MEC & User association and resource allocation & Optimize downlink utility & MDP & Multi-agent D3QN & Not consider system delay and energy consumtion \\\midrule
				\cite{sun2024hierarchical} & MEC & Computation offloading and service caching & Minimize average service delay & MDP & hierarchical DRL & Not consider system energy consumtion \\\midrule
				\cite{wu2023computation}  & SDN-based MEC & Stochastic game-based resource allocation & Minimize energy consumption and processing delay & MDP & Multi-agent RL & Not consider tasks with maximum delay tolerance\\\midrule
				\cite{dai2020edge} & MEC & Resource allocation and computation offloading & Minimize energy consumption & MDP & DDPG & Not take user's demand into consideration \\\midrule
				\cite{liu2021learn} & MEC & Resource allocation and computation offloading & Minimize execution cost & POMDP & Multi-agent actor-critic network &  Not consider delay-sensitive tasks \\\midrule
				\cite{gong2022edge} & MEC-based IIoT & Resource allocation and computation offloading & Minimize task computation delay and energy consumption & MDP & DRL & Not take user's demand into consideration\\\midrule
				\cite{gao2022large} & Queuing-based heterogeneous MEC & Decentralized computation offloading & Optimize system cost and completion rates & MDP & Multi-agent actor-critic network& Not take user's demand into consideration \\\midrule
				\cite{9253665} &  Queuing-based MEC &  Computation offloading & Minimize drop rate and computation delay. & MDP & D3QN + LSTM & Not consider system energy consumtion\\\midrule
				\cite{wu2024combining}  & Queuing-based IIoT MEC & Privacy aware computation offloading & Optimization of computation rate and energy consumption & MDP & Actor-critic network  & Not take user's demand into consideration \\\midrule
				\cite{wu2023multi} & Queuing-based IIoT MEC & Computation offloading & Optimize delay and energy consumption & POMDP & Multi-agent PPO&  Not consider tasks with maximum delay tolerance \\\midrule
				\cite{huang2021deadline} & Queuing-based MEC & Computation offloading & Optimize drop rate and energy consumption & POMDP & DDPG & Not consider computation delay \\ \midrule
				\cite{Bolourian-WCL24}  & Queuing-based MEC with EHs& Energy harvesting  computation offloading & Minimize drop rate and energy consumption. & MDP  & DQN & Not consider computation delay  \\\midrule
				QECO &  Queuing-based MEC &  Computation offloading & Maximize the QoE of each MD individually &MDP & D3QN + LSTM & \\
				\toprule
		\end{tabular}}
		\label{table1}}
\end{table*}

@@

We define $z_i(t)$ as the index assigned to the computation task arriving at MD $i \in \mathcal{I}$ in time slot $t \in \mathcal{T}$. Let $\lambda_i(t)$ denote the size of this task in bits. \textcolor{blue}{The size of task $z_i(t)$ is selected randomly from a discrete set $\Lambda = \{\lambda_1, \lambda_2, \ldots, \lambda_{\theta}\}$, where $\theta$ represents the number of these values.} Hence, $\lambda_i(t) \in \Lambda \cup \{0\}$ to consider the case that no task has arrived. We also denote the task's processing density as $\rho_i(t)$ that indicates the number of CPU cycles required to complete the execution of a unit of the task. Furthermore, we denote the deadline of this task by $\Delta_i(t)$ which is the number of time slots that the task must be completed to avoid being dropped.
%At the beginning of time slot $t \in \mathcal{T}$, if MD $i \in \mathcal{I}$ has a newly arrived task, we define $z_i(t)$ as the unique index assigned to that task. Let $\lambda_i(t)$ be the number of newly arrived bits at the beginning of time slot $t \in \mathcal{T}$. If a new task $z_i(t)$ exists at the start of time slot $t$, then $\lambda_i(t)$ is equal to the size of task $z_i(t)$. Otherwise, $\lambda_i(t) = 0$. We consider $\rho_i(t)$ to represent the processing density of task $z_i(t)$, indicating the number of CPU cycles required to process a unit of the task.

@@

In addition to the energy consumed by EN $j$ for task processing, we also take into account the energy consumed by the MD $i$'s user interface in the standby state while waiting for task completion at the EN $j$. We define $E_{i,j}^{\text{I}}(t)$ as the energy consumption associated with the user interface of MD $i \in \mathcal{I}$, which is given by
\begin{alignat}{1}
	E_i^{\text{I}}(t) = \textcolor{blue}{\sum_{\mathcal{J}} y_{i,j}(t)} D_{i,j}^{\text{E}}(t) p_i^{\text{I}} \tau, %= {\lambda_{i,j}^{\text{E}}(t) \rho_i(t) \over \mathcal{B}_j(t) f_j^{\text{E}}} p_i^{\text{I}},
	\label{16}
\end{alignat}
where $p_i^{\text{I}}$ is the standby energy consumption of MD $i \in \mathcal{I}$.
\begin{alignat}{1}
	E_i^{\text{O}}(t) = E_i^{\text{T}}(t) + \sum_{\mathcal{J}} \textcolor{blue}{y_{i,j}(t)} E_{i,j}^{\text{E}}(t) + E_i^{\text{I}}(t).
	\label{17}
\end{alignat}

@@

\item \textcolor{blue}{\textbf{DCDRL~\cite{qiu2020distributed}:} This method is a distributed optimization algorithm designed for delay-sensitive tasks in a queuing-based MEC environment, where MDs strategically interact with multiple ENs. We select DCDRL as a benchmark due to its similarity to our work. It is based on the actor-critic framework \cite{konda1999actor}, which underpins many state-of-the-art DRL algorithms, such as DDPG \cite{lillicrap2015continuous}, and PPO \cite{schulman2017proximal}}.

>>>>

\begin{table*}[htbp]\textcolor{blue}{
		\renewcommand{\arraystretch}{0.7}
		\captionsetup{name=TABLE}
		\caption{Comparison of Related Works}
		\scalebox{1}{%
			\begin{tabular}{ lp{2.2cm}p{3cm}p{3.4cm}p{0.7cm}p{2cm}p{3.2cm}l} 
				\toprule
				\textbf{Paper} & \textbf{Scenario} &  \textbf{Problem} &  \textbf{Objective} &  \textbf{Model} & \textbf{Method} &  \textbf{Drawbacks}  \\ \midrule
				\cite{liao2023online} & Queuing-based MEC & Online computation offloading & Minimize computation delay and energy consumption & MDP & DDQN & Only for a single MEC system model  \\\midrule
				\cite{zhou2021deep} & heterogeneous MEC & Resource allocation and computation offloading & Minimize energy consumption of the entire system & MDP & DDQN & Only for a single MEC system model \\\midrule				
				%\cite{huang2019deep} & Wireless-powered MEC & Computation offloading and resource allocations & Maximize computation rate & MIP & DQN & Not consider delay-sensitive tasks \\\midrule
				\cite{wu2024privacy} & MEC-based IIoT  & Joint power allocation and computation offloading  & Optimization of privacy protection and quality of service. & MDP & Multi-agent actor-critic network& Not take user's demand into consideration \\\midrule
				\cite{zhao2019deep} & MEC & User association and resource allocation & Optimize downlink utility & MDP & Multi-agent D3QN & Not consider system delay and energy consumtion \\\midrule
				\cite{sun2024hierarchical} & MEC & Computation offloading and service caching & Minimize average service delay & MDP & hierarchical DRL & Not consider system energy consumtion \\\midrule
				\cite{wu2023computation}  & SDN-based MEC & Stochastic game-based resource allocation & Minimize energy consumption and processing delay & MDP & Multi-agent RL & Not consider tasks with maximum delay tolerance\\\midrule
				\cite{dai2020edge} & MEC & Resource allocation and computation offloading & Minimize energy consumption & MDP & DDPG & Not take user's demand into consideration \\\midrule
				\cite{liu2021learn} & MEC & Resource allocation and computation offloading & Minimize execution cost & POMDP & Multi-agent actor-critic network &  Not consider delay-sensitive tasks \\\midrule
				\cite{gong2022edge} & MEC-based IIoT & Resource allocation and computation offloading & Minimize task computation delay and energy consumption & MDP & DRL & Not take user's demand into consideration\\\midrule
				\cite{gao2022large} & Queuing-based heterogeneous MEC & Decentralized computation offloading & Optimize system cost and completion rates & MDP & Multi-agent actor-critic network& Not take user's demand into consideration \\\midrule
				\cite{9253665} &  Queuing-based MEC &  Computation offloading & Minimize drop rate and computation delay. & MDP & D3QN + LSTM & Not consider system energy consumtion\\\midrule
				\cite{wu2024combining}  & Queuing-based IIoT MEC & Privacy aware computation offloading & Optimization of computation rate and energy consumption & MDP & Actor-critic network  & Not take user's demand into consideration \\\midrule
				\cite{wu2023multi} & Queuing-based IIoT MEC & Computation offloading & Optimize delay and energy consumption & POMDP & Multi-agent PPO&  Not consider tasks with maximum delay tolerance \\\midrule
				\cite{huang2021deadline} & Queuing-based MEC & Computation offloading & Optimize drop rate and energy consumption & POMDP & DDPG & Not consider computation delay \\ \midrule
				\cite{Bolourian-WCL24}  & Queuing-based MEC with EHs& Energy harvesting  computation offloading & Minimize drop rate and energy consumption. & MDP  & DQN & Not consider computation delay  \\\midrule
				QECO &  Queuing-based MEC &  Computation offloading & Maximize the QoE of each MD individually &MDP & D3QN + LSTM & \\
				\toprule
		\end{tabular}}
		\label{table1}}
\end{table*}

@@

We define $z_i(t)$ as the index assigned to the computation task arriving at MD $i \in \mathcal{I}$ in time slot $t \in \mathcal{T}$. Let $\lambda_i(t)$ denote the size of this task in bits. \textcolor{blue}{The size of task \( z_i(t) \) is selected randomly and uniformly from a discrete set \( \Lambda = \{\lambda_1, \lambda_2, \ldots, \lambda_{\theta}\} \), where \( \theta \) represents the number of these values. Note that task sizes are drawn from a discrete set since, in many applications, tasks typically come with predefined sizes. We consider, $\lambda_i(t) \in \Lambda \cup \{0\}$ to include the case that no task has arrived.} We also denote the task's processing density as $\rho_i(t)$ that indicates the number of CPU cycles required to complete the execution of a unit of the task. Furthermore, we denote the deadline of this task by $\Delta_i(t)$ which is the number of time slots that the task must be completed to avoid being dropped.
%At the beginning of time slot $t \in \mathcal{T}$, if MD $i \in \mathcal{I}$ has a newly arrived task, we define $z_i(t)$ as the unique index assigned to that task. Let $\lambda_i(t)$ be the number of newly arrived bits at the beginning of time slot $t \in \mathcal{T}$. If a new task $z_i(t)$ exists at the start of time slot $t$, then $\lambda_i(t)$ is equal to the size of task $z_i(t)$. Otherwise, $\lambda_i(t) = 0$. We consider $\rho_i(t)$ to represent the processing density of task $z_i(t)$, indicating the number of CPU cycles required to process a unit of the task.

@@

In addition to the energy consumed by EN $j$ for task processing, we also take into account the energy consumed by the MD $i$'s user interface in the standby state while waiting for task completion at the EN $j$. We define $E_{i,j}^{\text{I}}(t)$ as the energy consumption associated with the user interface of MD $i \in \mathcal{I}$, which is given by
\begin{alignat}{1}
	E_{i,j}^{\text{I}}(t) =  D_{i,j}^{\text{E}}(t) p_i^{\text{I}} \tau, %= {\lambda_{i,j}^{\text{E}}(t) \rho_i(t) \over \mathcal{B}_j(t) f_j^{\text{E}}} p_i^{\text{I}},
	\label{16}
\end{alignat}
where $p_i^{\text{I}}$ is the standby energy consumption of MD $i \in \mathcal{I}$.
\begin{alignat}{1}
	E_i^{\text{O}}(t) = E_i^{\text{T}}(t) + \sum_{\mathcal{J}} \textcolor{blue}{y_{i,j}(t)} E_{i,j}^{\text{E}}(t) + E_i^{\text{I}}(t).
	\label{17}
\end{alignat}

@@

\item \textcolor{blue}{\textbf{DCDRL}~\cite{qiu2020distributed}: This method is based on the actor-critic framework \cite{NIPS1999_6449f44a}, which underpins many state-of-the-art DRL algorithms, such as DDPG \cite{lillicrap2015continuous}, and PPO \cite{schulman2017proximal}. This method is a distributed algorithm designed for delay-sensitive tasks in a queuing-based MEC environment, where MDs strategically interact with multiple ENs. We select DCDRL as a benchmark due to its similarity to our work.}
